Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-02-04 Ben_Manuscripts/transport/Outline.tex
outline edits and renaming

  There is a broad range of water concentrations which will form a stable 
  H\textsubscript{II} phase with Na-GA3C11. 
  \begin{itemize}
	\item In the literature this system is typically synthesized with close
	to 10 wt \% water
        \item However, Resel et al. noted that the system is likely fully 
	hydrated with less than 7 wt \% water.
	\item We decided to test two different levels of water content: 5 and 10 wt \%
  \end{itemize}

  %MRS: may need to discuss the fact that the amount of water present in the tails may 
  %MRS: or may not be experimentally consistent; but if we don't put it in, the results will 
  %MRS: not be thermodynamically consistent, which will give issues with measurements and calculations.
  %MRS2: hopefully, some experiments could let us know about different diffusion regimes . . . 
  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work (reference to structure
	paper).
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimzation.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using long simulations, on the order of
	1 microsecond
	\item .mdp files are in the supporting information % with pressure controlled by the Parrinello-Rahman barostat.
  \end{itemize}

  \subsubsection*{Modeling the Continuous Time Random Walk}\label{method:CTRW}

  A continuous time random walk (CTRW) is a stochastic anomalous diffusion
  process characterized by a distribution of hop lengths and dwell times.
  \begin{itemize}
	\item The MSD for an anomalous diffusion process is of the form
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient. 
	\item A value of $\alpha < 1$ indicates a subdiffusive process.
	\item Subdiffusive, non-ergodic processes with uncorrelated steps distinguish 
	a CTRW from other anomalous subdiffusive process such as fractional brownian motion 
	and random walks on a fractal.~\cite{meroz_toolbox_2015}
	\item See supporting info for proof of the system's non-ergodicty and uncorrelated steps.
  \end{itemize}

  We obtained maximum likelihood estimates (MLE) of the parameters used to fit our
  emperical dwell and hop length distributions to analytical functions.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories. (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item The corresponding hop lengths and dwell times between break points were 
	used to construct emperical distributions.
	\item For solutes in our system the distribution of hop lengths is
	well-represented by a Gaussian distribution (Which has been often used in
	literature)
	\item The maximum likelihood estimate of Gaussian parameters is given simply
	by the mean and standard deviation of the emperical data.
	~\cite{metzler_random_2000,metzler_anomalous_2014,neusius_subdiffusion_2009} 
	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	emperical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
        \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powelaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	%\item Incorporates effects of `aging' since it samples long dwell times
  \end{itemize}

  %BJC: not sure following explanation is necessary. Could put thesis statement
  % in previous paragraph.
  We generated distributions of parameters for the dwell time and hop length
  distributions using statistical bootstrapping.
  \begin{itemize}
	\item For each type of distribution, we randomly selected $n$ data points from the emperical
	distribution with replacement.
	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
  \end{itemize}

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  We simulated trajectories order of magnitude longer than our molecular simulations. 
  \begin{itemize}
	\item We constructed 10000, 10000 timestep trajectories by generating
	sequences of dwell times and hop lengths randomly sampled from the appropriate
	distributions.
	\item For each trajectory, the parameters used to define each distribution were
	randomly drawn from the bootstrapped parameter distributions.
	\item We randomly sample Gaussian hop lengths using the
	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
	\item We randomly sampled dwell times from a discrete power law
	distribution based on the reccomendations of Clauset et
	al.~\cite{clauset_power-law_2009}: 
	\begin{equation}
	x = \lfloor
	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
	\label{eqn:discrete_powerlaw_draws}
	\end{equation}
	where $r$ is randomly drawn from a uniform distribution which we simulated
	with \texttt{numpy.random.uniform}.
	\item We found that thermal noise does not significantly influence the MSD and
	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

  We calculated both the ensemble-averaged and time-averaged mean squared displacements (MSDs)
  of the simulated trajectories.
  \begin{itemize}
	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
	position ~\cite{meroz_toolbox_2015} and can be written as
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
	\item The average MSD calculated in this way recovers the form of
	Equation~\ref{eqn:msd_form}. 
	\item The time-averaged MSD measures the displacement between all possible time lags
	and can be written as
	\begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}{T - \tau} (x(t + \tau) - x(t))^2 dt
	\end{equation}
	where $\tau$ is the time lage and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
	\item The time-averaged MSD becomes linear in our simulations,
	therefore we can fit a line to its slope in order to estimate the macroscopic
	diffusivity of the particle.
	%BJC: this needs more justification. Not many people have done it
	%BJC: could also not report them as diffusivities. Comparison of total MSD
	% should give same information
	% Linear region probably exists because dwell times on the order of large lag times
	% become negligible
  \end{itemize}

  We fixed the length of each simulated trajectory so that we could compare the total
  MSD between different solutes without the influence of the ageing phenomenon.
  \begin{item}
	\item Ageing is defined by the tendency of the average MSD to decrease
	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
	\item The maximum measured dwell time can be no longer than the total length
	of a simulated trajectory. 
	\item As measurement time or trajectory length is increased, longer dwell times
	are incorporated into the calculation, lowering the average MSD. (See supporting
	info for demonstration)
	\item We can achieve consistent total MSDs with low uncertainty for
	simulated trajectories created with a given set of parameters if we fix the
	trajectory length (as opposed to total number of steps).  
  \end{item}

@@

  We quantified the coordination of solutes with surrounding molecules.
  \begin{itemize}
  	\item For each frame, we counted the identites and number of
  	coordinated molecules to a given solute based on a distance cut-off. 
	\item We found that this approach is more useful than calculating the
	3D spherical radial distribution function because it gives detailed
	frame-by-frame information rather than an average. 
  \end{itemize}

  \subsection{Experimental}
  % BJC: For Greg to write if things work out

@@

  \subsection{Simulated Predictions}\label{section:D_macro}

  Polar molecules generally exhibit a hop diffusion mechanism. 
  \begin{itemize}
	\item Each trajectory is characterized by a power law distribution of
	dwell times between hops of random lengths from a Gaussian distribution.
  \end{itemize}

  % BJC: figure with selected trajectories for each molecule.

  We fit a CTRW model (see Section~\ref{method:CTRW}) to these 
  trajectories and predicted macroscopic diffusion coefficients which are
  presented in Table TBD.
  \begin{itemize}
	\item We confirmed that our molecules exhibit anomalous diffusion
	by fitting a power law to the MSD curve. The exponent is less than
	1, indicative of anomalous subdiffusion.
	\item We used the decision making process given by Meroz and Sokolov
	in order to identify the appropriate subdiffusion model to use 
	based on our time series (See Section S-TBD of the Supporting info for
	more details).
	\item The motion of the solutes is non-ergodic and the steps are
	uncorrelated which tells us the system is likely well-described
	by a CTRW. 
  \end{itemize}

  % BJC: table with finalized diffusion coefficients

@@

  \bibliographystyle{ieeetr}
  \bibliography{Transport}

>>>>

  Stable H\textsubscript{II} phases, assembled with Na-GA3C11, can be formed
  using a broad range of water concentrations.
  \begin{itemize}
	\item In the literature, this system is typically synthesized with close
	to 10 wt \% water \cite{smith_ordered_1997, zhou_new_2007}
    \item However, Resel et al. noted that the system is likely fully 
	hydrated with less than 7 wt \% water. \cite{resel_h2-phase_2000}
	\item We decided to test two different levels of water content: 5 and 10 wt \%
  \end{itemize}

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimization.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using 1 $\mu$s simulations
  \end{itemize}

%  \subsubsection*{Modeling subdiffusion}\label{method:model_sFBM}
%
%  Solutes in our H\textsubscript{II} LLC membrane exhibit subdiffusive
%  behavior, a type of anomalous diffusion. 
%  \begin{itemize}
%  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
%  	does not grow linearly with time, rather it is of the form:
%	\begin{equation} 
%	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
%	\label{eqn:msd_form}
%	\end{equation} 
%	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
%	generalized diffusion coefficient.
%	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
%	$\alpha = 1$ and $\alpha > 0$ is characteristic of Brownian and superdiffusive
%	motion respectively.
%  \end{itemize}
%
%  \noindent We calculated both the ensemble-averaged and time-averaged MSDs
%  of the simulated trajectories.
%  \begin{itemize}
%	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
%	position~\cite{meroz_toolbox_2015} and can be written as
%	\begin{equation}
%	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
%	\label{eqn:ensemble_msd}
%	\end{equation}
%%	\item The average MSD calculated in this way recovers the form of
%%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
%	\item The time-averaged MSD measures the displacement between all possible time lags
%	and can be written as
%	\begin{equation}
%	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
%	\end{equation}
%	where $\tau$ is the time lag and T is the length of the
%	trajectory~\cite{meroz_toolbox_2015}. 
%%	\item The time-averaged MSD becomes linear in our simulations,
%%	therefore we can fit a line to its slope in order to estimate the macroscopic
%%	diffusivity of the particle.
%	%BJC: this needs more justification. Not many people have done it
%	%BJC: could also not report them as diffusivities. Comparison of total MSD
%	% should give same information
%	% Linear region probably exists because dwell times on the order of large lag times
%	% become negligible
%  \end{itemize}
%  
%  \noindent Three common mathematical models for modeling anomalous subdiffusion processes include 
%  continuous time random walks (CTRW), fractional Brownian motion (FBM) and
%  random walks on fractals (RWF).\cite{meroz_toolbox_2015}
%  \begin{itemize}
%    \item FBM is common in crowded, viscoelastic environments where each step comes 
%    from a Gaussian distribution but is anti-correlated to its previous 
%    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%    \item A CTRW is characterized by a distribution of hop lengths and 
%    dwell times, where each each step is characterized by independent random draws from 
%    each distribution.\cite{montroll_random_1965,morrin_three_2018}
%    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
%    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
%    \item The processes described above can happen alone or in combination.  	
%  \end{itemize}
%  
%  \noindent We believe that solutes in the system studied here exhibit subordinated 
%  fractional Brownian motion (sFBM) where the parent process is FBM and the 
%  leading process is a CTRW. 
%  \begin{itemize}
%  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
%  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
%  	\item We also observe non-stationary $z$-coordinate traces of each solute's
%  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
%  	\item For a pure CTRW, the time-averaged MSD should be linear.
%  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
%  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
%  	information), which suggests that there is another underlying subdiffusive mechanism.
%  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
%  	\item Given the viscoelastic nature of the monomers in our system, we believe
%  	the hop lengths can be modeled with FBM. 
% 	\item For subordinated FBM, it can be shown that
%  	\begin{equation}
%  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
%  	\end{equation}
%  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
%  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
%  \end{itemize}
%
%  \noindent We can characterize a CTRW process using the parameters which describe its
%  dwell time and hop length distribution.
%  \begin{itemize}
%	\item We used the \texttt{ruptures} python package in order to identify
%	breakpoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting Information for more
%	details on chosen parameters. i.e. type of cost function, cost function penalty
%	tolerance, number of dimensions used)
%	\item The corresponding hop lengths and dwell times between break points were 
%	used to construct empirical distributions.
%	\item For solutes in our system, the distribution of hop lengths is
%	well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
%	metzler_anomalous_2014,neusius_subdiffusion_2009}
%	\item We are most interested in the standard deviation, $\sigma$, of the 
%	hop length distribution.
%	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
%	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
%	\item Because we are limited to taking measurements at discrete values
%	dictated by the output frequency of our simulation trajectories, we fit the
%	empirical dwell times to a discrete power law distribution whose maximum
%	likelihood $\alpha$ parameter we calculated by maximizing the following
%	likelihood function: 
%        \begin{equation}
%	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
%	\beta\sum_{i=1}^{n} \text{ln}~x_i 
%	\label{eqn:powerlaw_likelihood}
%	\end{equation}
%	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
%	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
%	where $x_{min}$ is the smallest measured value of
%	$x_i$.~\cite{clauset_power-law_2009} 
%	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
%	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
%  \end{itemize}
%  
%  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
%  $H = \beta/2$.
%  \begin{itemize}
%  	\item Brownian motion is recovered for $H = 0.5$
%	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
%    \begin{equation}
%	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
%	\label{eqn:autocovariance}
%	\end{equation}
%	where $k$ is the number of increments between hops.
%	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
%	to the empirically measured autocovariance function.
%	\item We used statistical bootstrapping to generate a distribution of $H$ 
%	values. %BJC: can provide more detail in supporting or just reference python script
%  \end{itemize}
%
%%  We generated distributions of parameters for the dwell time and hop length
%%  distributions using statistical bootstrapping.
%%  \begin{itemize}
%%	\item For each type of distribution, we randomly selected $n$ data points from the empirical
%%	distribution with replacement.
%%	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
%%  \end{itemize} 
%
%%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%%  magnitude longer than our molecular simulations.
%  \noindent For each solute, we simulated 10000 sFBM trajectories for 1 $\mu$s each. 
%  \begin{itemize}
%	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
%	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
%	distributions.
%	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
%	the last data point so that the total time exactly equaled 1 $\mu$s. 
%    \item Valid comparisons are only possible between fixed length sFBM simulations. The
%    power law dwell time behavior gives rise to the aging phenomenon, embodied by
%    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
%    \item We reported the MSD after 1 $\mu$s with corresponding 95 \% intervals
%% Following probably better suited for supporting information, if included at all
%%	\item We randomly sample Gaussian hop lengths using the
%%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%%	\item We randomly sampled dwell times from a discrete power law
%%	distribution based on the recommendations of Clauset et
%%	al.~\cite{clauset_power-law_2009}: 
%%	\begin{equation}
%%	x = \lfloor
%%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%%	\label{eqn:discrete_powerlaw_draws}
%%	\end{equation}
%%	where $r$ is randomly drawn from a uniform distribution which we simulated
%%	with \texttt{numpy.random.uniform}.
%%	\item We found that thermal noise does not significantly influence the MSD and
%%	therefore did not add any noise to the simulated trajectories. (See supporting info)
%  \end{itemize}
%
%%BJC: probably don't need to explain this in great detail
%%  \noindent We fixed the length of each simulated trajectory so that we could compare the total
%%  MSD between different solutes without the influence of the ageing phenomenon.
%%  \begin{itemize}
%%	\item Ageing is defined by the tendency of the average MSD to decrease
%%	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
%%	\item The maximum measured dwell time can be no longer than the total length
%%	of a simulated trajectory. 
%%	\item As measurement time or trajectory length is increased, longer dwell times
%%	are incorporated into the calculation, lowering the average MSD. (See supporting
%%	info for demonstration)
%%	\item We can achieve consistent total MSDs with low uncertainty for
%%	simulated trajectories created with a given set of parameters if we fix the
%%	trajectory length (as opposed to total number of steps).  
%%  \end{itemize}

@@

  We quantified the coordination of solutes with surrounding molecules.
  \begin{itemize}
  	\item For each frame, we counted the identities and number of
  	coordinated molecules to a given solute based on a distance cut-off. 
	\item We found that this approach is more useful than calculating the
	3D spherical radial distribution function because it gives detailed
	frame-by-frame information rather than an average. 
  \end{itemize}

@@

  \subsection{Governing Mechanisms}\label{section:mechanism_overview}

  % BJC: seems right to summarize overarching mechanisms observed first  
  On the timescales simulated in our study, solutes exhibit subdiffusive
  transport behavior as evidenced by their sublinear MSD curves. 
  \begin{itemize}  
	\item As an example, the MSD curve for ethanol is plotted in 
	Figure~\ref{fig:example_msd}.
  \end{itemize}

  \noindent All solutes exhibit hop diffusion, characteristic of a continuous time random walk.
  \begin{itemize}
  	\item Figure~\ref{fig:example_ztraces} shows the $z$-coordinate versus time of
  	3 representative ethanol centers of mass.
  	\item There are clear periods of entrapment separated by relatively large hops.
  	\item The length of entrapment follows a power law distribution 
  	(Figure~\ref{fig:example_powerlaw}) and the distribution of hop lengths can be 
  	described with a Gaussian distribution (Figure~\ref{fig:example_hop_dist}).
  	\item Power law distributed dwell times are responsible for the ageing phenomenon
  	which causes the MSD curve to decrease with increasing measurement time as longer
  	dwell times get sampled.
  \end{itemize}

  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
  \begin{itemize}
  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Better word?
  	\item The negative autocovariance at low values of k indicates anti-correlation
  	between steps. 
  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
  	decay to zero immediately.
  	\item Although the autocovariance function is relatively noise, due to the somewhat small
  	number of hops observed over the course of each solute trajectory, there is the least 
  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
  	all solutes molecules.
  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
  	motion where the leading process is a CTRW with hops that are dictated by the parent
  	process, FBM.
  	\item Future publications will focus on modeling the solute's transport characteristics
  	with an sFBM model
  \end{itemize}

% BJC: first iteration of figure after this before I decided to include a hop length and dwell time distribution
%  \begin{figure}
%  \centering
%  \includegraphics[width=\textwidth]{msd_ztrace_acf.pdf}
%  \caption{}\label{fig:msd_ztrace_acf}
%  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \par\medskip
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{example_powerlaw.pdf}
  \caption{}\label{fig:example_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{example_hop_dist.pdf}
  \caption{}\label{fig:example_hop_dist}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{example_autocovariance.pdf}
  \caption{}\label{fig:example_autocovariance}
  \end{subfigure}
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The time-averaged MSD of 
  ethanol is not linear which suggests transport is governed by an anomalous 
  subdiffusion process. (b) The $z$-coordinate trace of 3 representative ethanol
  COMs shows clear periods of entrapment separated by hops. (c) The distribution
  of dwell times follows a power law. (d) The distribution of hop lengths appears
  Gaussian. (e) Hops are anti-correlated to their previous hop as indicated by the
  negative value of the autocovariance function at $k$ = 1.}\label{fig:examples}
  \end{figure}

  % BJC: would it be better to report as a fraction of water MSD?
  \noindent We calculated the time-averaged MSD of each solute in the set over the
  course of 1 $\mu$s MD simulations. 
  \begin{itemize}
    \item Because the MSDs are non-linear and because of the ageing phenomenon, we
    did not attempt to calculate a diffusion constant as one might for a Brownian
    particle with a linear MSD.
	\item Instead, the values plotted in Figure~\ref{fig:all_msds} represent the
	average MSD of each solute after a 400 ns time lag.
  \end{itemize}

  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{all_tamsds.pdf}
  \caption{}\label{fig:all_msds}
  \end{figure}

  \noindent The MSDs in Figure~\ref{fig:all_msds} are a strong function of two solute 
  trapping mechanisms. % by which solutes become trapped.
  \begin{itemize}
  	\item Solutes that are hydrogen bond donors can be stabilized through hydrogen bonds
  	with one of the five oxygen atoms attached to each monomer head group. 
  	\item In a separate interaction, solutes can become kinetically trapped between 
  	monomer head groups.
  	\item Generally, both mechanisms affect each solute to varying degrees.
  \end{itemize}

  %BJC: somewhere need to say why solutes preferentially hbond with carboxylate groups -- is this real

  \noindent A solute's size, shape, and polarity dictate the degree to which they 
  are influenced by each entrapment mechanism.
  \begin{itemize}
    \item In general, solutes can move fastest in the pore center, where
    there is comparatively little resistance to diffusion.
%    \item The smallest molecular weight solutes move fastest.
    \item Low molecular weight, highly water-soluble, hydrogen bond donating molecules spend the most time
    in the pore center where they are slowed down primarily by hydrogen bonds
    with monomer carboxylate groups.
    %BJC: this isn't fully accurate yet. Need to come back to this
    \item Solutes that cannot donate hydrogen bonds, or are less miscible in water, 
    tend to partition into the head group region where entrapment occurs. Most of
    the anti-correlated motion occurs here.
    \item The inverse relationship between solute size and mobility is disrupted
    by solutes' preference for water. 
    \item We observe low MW solutes with lower-than-expected MSDs because they
    spend more time trapped between monomer head groups due to low water
    solubility.
    \item Small, planar molecules exhibit some of the shortest MSDs because

  	\item The well-established trend of decreasing solute mobility with 
  	size is not defied here, however 
  	\item Additionally, planar molecules are prone to exhibiting similar
  	trapping behavior, even for large molecules whose similar sized, but flexible
  	counterparts exhibit faster diffusion.  %BJC: this is unproven
  	\item The polarity of solutes also influences a solute's ability to stay in
  	the pore center. Highly polar molecules tend to spend more time in the pore center,
  	while those with hydrophobic character tend to spend more time in the head group
  	region.
  	\item Finally, the ability to hydrogen bond offers a second trapping mechanism. 
  	Solutes that are hydrogen bond donors can donate hydrogen atoms to
  	any of the 5 oxygen atoms located on the monomer head groups. Increasing the 
  	number of hydrogen bond donating groups increases the solute's polarity causing
  	solutes to spend more time in the pore centers, but the effect can be countered
  	by excessive trapping if there are many hydrogen bonds being formed.
  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
  	mechanisms, with anticorrelated hops between each period of immobility due to 
  	obstructions.
  \end{itemize}

  We will revisit these observations in the the context of specific groups of 
  molecules in the discussion that follows.

%  We will explore these factors in greater detail in the context of 
%  specific groups of molecules in the discussion that follows.

  \subsection{Mean Squared Displacement Predictions}\label{section:msd_predictions}

  %BJC: focus on MD MSD results

@@

  \bibliographystyle{ieeetr}
  \bibliography{transport}
